Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-30 Codes/PrepareResults.rmd

# === Data === #
field_subplot_test_dt <-
  readRDS(here("Shared/Results/for_writing/field_subplot_test_dt.rds"))

train_dt <-
  field_subplot_sf %>%
  data.table()

test_dt <-
  field_subplot_test_dt %>%
  data.table()

@@

RF <-
  RF_run(
    reg_data = train_dt,
    var_ls = temp_var_ls
  )

BRF <-
  BRF_run(
    reg_data = train_dt,
    var_ls = temp_var_ls
  )

# === Yield prediction === #
# --- All N experimental rates --- #
N_rate <- test_dt[, aa_n] %>%
  unique() %>%
  sort()
# For illustration purpose, we use site where either 2nd and 4th N rates are actually application
tg_N_rate <- N_rate[c(2, 3, 4)]

# --- for true yield response function --- #
seq_N <-
  seq(min(N_rate) - 30, max(N_rate) + 30, by = 1)
# seq_N <-
#   seq(min(N_rate), max(N_rate), by=1)

res_true <-
  test_dt %>%
  .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = unique_subplot_id] %>%
  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[, yield := det_yield * (1 + m_error)]

# --- for predicted yield at five experimental N rates --- #
res_pred <-
  test_dt %>%
  .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(N_rate)), ] %>%
  .[, N := N_rate, by = unique_subplot_id] %>%
  .[, RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  .[, BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  melt(id.vars = c("unique_subplot_id", "yield", "aa_n", "N"), measure.vars = c("RF", "BRF"))

find_examples_main <-
  res_pred %>%
  .[variable == "BRF" & aa_n == N, ] %>%
  .[, y_diff_brf := abs(yield - value)] %>%
  .[y_diff_brf < 500, unique_subplot_id]
# .[y_diff_brf < 500 & y_diff_brf < 1000, unique_subplot_id]

# === For visualization === #
# set.seed(1256)

# low <-
#   res_true[aa_n == tg_N_rate[3]] %>%
#   get_rows_optN(data=., value = 0.9, range = 0.1) %>%
#   .[unique_subplot_id %in% find_examples_main] %>%
#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
#   .[, unique_subplot_id] %>%
#   unique()

# length(low)
# x <- 16
# i= x:(x+1)
# vis_res_true <- res_true[unique_subplot_id %in% low[i]]
# vis_res_pred <- res_pred[unique_subplot_id %in% low[i]]
# ggplot() +
#     geom_line(
#       data=vis_res_true, aes(x=N, y=yield, color = unique_subplot_id)
#     ) +
#     geom_point(
#       data=vis_res_pred, aes(x=N, y=value, color = unique_subplot_id, alpha = "Predicts"), shape=2, size = 1.5
#     ) +
#     geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
#     facet_wrap(~variable) +
#     scale_alpha_manual(
#       name = NULL,
#       values = c(1, 1),
#       breaks = c("Predicts", "True yield at actual N rate that was applied"),
#       guide = guide_legend(override.aes = list(linetype = c(0, 1),
#         shape = c(2, 16),
#         color = c("black", "blue"))
#         )
#     ) +
#     labs(y = "Yield (kg/ha)") +
#     labs(x = "N (kg/ha)") +
#     theme_dist +
#     theme(legend.title = element_blank()) +
#     guides(color=guide_legend(nrow=2, byrow=TRUE))

# tg_N_rate <- N_rate[2]
# low: 13_41, 15_34, 15_35, 11_40
# medium: 8_41, *8_42*, *8_43*, 27_10
# high: 4_21

# tg_N_rate <- N_rate[3]
# **2_18**, 10_42 ***6_47***

# tg_N_rate <- N_rate[4]
# 10_49

# final
# + *2_18* (more than 14500)
# + *8_42* (11500)
# + *8_43* (11300)
# + **6_47** (11100)

# c("2_18", "8_42")
# c("2_18", "6_47") **

# vis_res_true <- res_true[unique_subplot_id %in% c("2_18", "6_47")]
# vis_res_pred <- res_pred[unique_subplot_id %in% c("2_18", "6_47")]
# ggplot() +
#     geom_line(
#       data=vis_res_true, aes(x=N, y=yield, color = unique_subplot_id)
#     ) +
#     geom_point(
#       data=vis_res_pred, aes(x=N, y=value, color = unique_subplot_id, alpha = "Predicts"), shape=2, size = 1.5
#     ) +
#     geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
#     facet_wrap(~variable) +
#     scale_alpha_manual(
#       name = NULL,
#       values = c(1, 1),
#       breaks = c("Predicts", "True yield at actual N rate that was applied"),
#       guide = guide_legend(override.aes = list(linetype = c(0, 1),
#         shape = c(2, 16),
#         color = c("black", "blue"))
#         )
#     ) +
#     labs(y = "Yield (kg/ha)") +
#     labs(x = "N (kg/ha)") +
#     theme_dist +
#     theme(legend.title = element_blank()) +
#     guides(color=guide_legend(nrow=2, byrow=TRUE))

vis_res_true <-
  res_true[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[, site := case_when(
    unique_subplot_id == "2_18" ~ "site 1",
    unique_subplot_id == "6_47" ~ "site 2"
  )]

vis_res_pred <-
  res_pred[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[, site := case_when(
    unique_subplot_id == "2_18" ~ "site 1",
    unique_subplot_id == "6_47" ~ "site 2"
  )] %>%
  .[, type := "Predicted"] %>%
  .[, observed := ifelse(
    aa_n == N,
    "Observed Rate",
    "Unobserved Rate"
  )] %>%
  setnames("variable", "model") %>%
  .[, .(N, value, type, observed, model, site)]

vis_true_points <-
  vis_res_true[N %in% unique(vis_res_pred$N), ] %>%
  .[, type := "True"] %>%
  .[, observed := ifelse(
    aa_n == N,
    "Observed Rate",
    "Unobserved Rate"
  )] %>%
  setnames("yield", "value") %>%
  .[rep(1:.N, 2), ] %>%
  .[, model := c("RF", "BRF") %>% rep(each = 10)] %>%
  .[, .(N, value, type, observed, model, site)]

@@

```{r make-plot-MB-BRF-y}
vis_MB_BRF_y <-
  ggplot() +
  # --- true yield response curve --- #
  geom_line(
    data = vis_res_true,
    aes(x = N, y = yield, group = site)
  ) +
  geom_point(
    data = vis_all_points,
    aes(y = value, x = N, color = observed, shape = type),
    size = 2
  ) +
  geom_line(
    data = vis_all_points[type == "Predicted", ],
    aes(y = value, x = N, color = site),
    linetype = 2,
    size = 0.5
  ) +
  geom_vline(
    xintercept = vis_res_true$aa_n %>% unique(),
    color = "red",
    linetype = 2,
    size = 0.3
  ) +
  annotate(
    "text",
    x = 180, y = 9400,
    label = "Observed Rate \n = 150 (kg/ha)",
    family = "Times",
    size = 3
  ) +
  scale_shape_manual(
    values = c("Predicted" = 2, "True" = 16),
    name = "Yield Type"
  ) +
  scale_color_manual(
    values = c(
      "Observed Rate" = "red",
      "Unobserved Rate" = "blue"
    ),
    name = ""
  ) +
  facet_grid(. ~ model) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  guides(color = "none") +
  theme_dist
```

>>>>

# --- Data --- #
test_subplot_dt <- 
  here("Shared/Results/for_writing/test_subplot_dt.rds") %>%
  readRDS()

# subplots_infiled <- test_subplot_dt[,unique_subplot_id] %>% unique()

# cnn_pred <- 
#   here("Shared/Results/CNN_rawRes_onEval/alldata_model4.csv") %>%
#   fread() %>%
#   .[, c("subplot_id", "strip_id") := tstrsplit(id, "_", fixed=TRUE)] %>%
#   .[,unique_subplot_id := paste0(strip_id,"_",subplot_id)] %>%
#   .[sim==x & unique_subplot_id %in% subplots_infiled,] %>%
#   .[,.(sim, unique_subplot_id, rate, pred)] %>%
#   setnames(names(.), c("sim", "unique_subplot_id", "N", "CNN"))

@@

RF <-
  RF_run(
    reg_data = data.table(field_subplot_sf),
    var_ls = temp_var_ls
  )

BRF <-
  BRF_run(
    reg_data = data.table(field_subplot_sf),
    var_ls = temp_var_ls
  )

# /*===== Yield Calculation =====*/
# --- All N experimental rates --- #
N_rate <- test_subplot_dt[, aa_n] %>% unique() %>% sort()

# --- for true yield response function --- #
seq_N <-
  seq(min(N_rate) - 30, max(N_rate) + 30, by = 1)

res_true <-
  test_subplot_dt %>%
  # .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = unique_subplot_id] %>%
  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[, yield := det_yield * (1 + m_error)]

# --- for predicted yield at five experimental N rates --- #
res_pred <-
  test_subplot_dt %>%
  # .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(N_rate)), ] %>%
  .[, N := N_rate, by = unique_subplot_id] %>%
  .[, RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  .[, BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  # .[cnn_pred, on = c("sim", "unique_subplot_id", "N")] %>%
  melt(
    id.vars = c("unique_subplot_id", "yield", "aa_n", "N"),
    # measure.vars = c("RF", "BRF", "CNN")
    measure.vars = c("RF", "BRF")
    ) %>%
  .[, observed := ifelse(
    aa_n == N,
    "Observed",
    "Unobserved"
  )] %>%
  .[, y_diff := abs(yield - value)]

# /*===== Preparation for plots =====*/
# new one
# c("8_43", "2_20")
# old one
# c("2_18", "6_47")

vis_res_true <-
  res_true[unique_subplot_id %in% c("2_18", "6_47")]

vis_res_pred <-
  res_pred[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[, type := "Predicted"] %>%
  setnames("variable", "model") %>%
  .[, .(N, value, type, observed, model, unique_subplot_id)]

vis_true_points <-
  vis_res_true %>%
  .[N %in% unique(vis_res_pred$N), ] %>%
  .[, type := "True"] %>%
  .[, observed := ifelse(
    aa_n == N,
    "Observed Rate",
    "Unobserved Rate"
  )] %>%
  setnames("yield", "value") %>%
  .[rep(1:.N, 2), ] %>%
  .[, model := c("RF", "BRF") %>% rep(each = 10)] %>%
  .[, .(N, value, type, observed, model, unique_subplot_id)]

@@

```{r make-plot-MB-BRF-y}
vis_MB_BRF_y <-
  ggplot() +
  # --- true yield response curve --- #
  geom_line(
    data = vis_res_true,
    aes(x = N, y = yield, group = unique_subplot_id)
  ) +
  geom_point(
    data = vis_all_points,
    aes(y = value, x = N, color = observed, shape = type),
    size = 2
  ) +
  geom_line(
    data = vis_all_points[type == "Predicted", ],
    aes(y = value, x = N, color = unique_subplot_id),
    linetype = 2,
    size = 0.5
  ) +
  geom_vline(
    xintercept = vis_res_true$aa_n %>% unique(),
    color = "red",
    linetype = 2,
    size = 0.3
  ) +
  # annotate(
  #   "text",
  #   x = 137,  y = 9700,
  #   label = "Observed Rate \n = 117 (kg/ha)",
  #   family = "Times",
  #   size = 2
  # ) +
  annotate(
    "text",
    x = 180, y = 9400,
    label = "Observed Rate \n = 150 (kg/ha)",
    family = "Times",
    size = 3
  ) +
  scale_shape_manual(
    values = c("Predicted" = 2, "True" = 16),
    name = "Yield Type"
  ) +
  scale_color_manual(
    values = c(
      "Observed Rate" = "red",
      "Unobserved Rate" = "blue"
    ),
    name = ""
  ) +
  facet_grid(. ~ model) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  guides(color = "none") +
  theme_dist
```

### 2022-03-30 Writing/manuscript_cea.rmd

The first term on the right-hand side of Eq. \@ref(eq:eqn3) is the deterministic yield component. The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot. Also in Eq. \@ref(eq:eqn3), $\alpha$, $\beta$, and $ymax$ are spatially varying parameters that govern how yield level is determined in conjunction with the applied N rate. They reflect local cell-level production conditions, such as soil characteristics and topography. For example, $\alpha$, which represents what the yield would be when no nitrogen is applied in conjunction with $ymax$, may reflect soil organic matter and residual nitrogen from previous year's production. $ymax$, which determines the maximum yield attainable, may include other micro nutrients like phosphorus and soil depth. $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen]. Figure \@ref(fig:vis-MB-curve) presents example visualization of site-specific yield response fuctions for some sites.

@@

CNN leaves room for researchers to determine its architecture. We used a slightly modified version of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion." Briefly stated, explanatory variables except N rate (e.g. $\alpha_{i,j}$, $\beta_{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.The input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot. First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters each with stride one, followed by a $2 \times 2$ max-pooling layer with stride two. Then, a fully-connected rectified linear unit (ReLU) layer with sixteen neurons was added after each max-pooling layer, followed by a single ReLU neuron. Finally, multiple neurons were concatenated and fed to the fully-connected ReLU layer with sixteen neurons, followed by an output with a linear activation function. @barbosa2020modeling demonstrated that among several CNN architectures, this architecture modeled crop yield response to N rate management best. CNN was implemented in Python v3.7.6 using Pytorch v1.7.0 [@paszke2017automatic]. The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value). To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience (see Figure \@ref(cnn-epoch) for an illustration of the convergens of training with respect to the number of epochs).

@@

Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the RMSEs of the EONR estimations and $\hat{\pi}_{def}$ obtained from the 1000 simualtion rounds by ML method and modeling scenario, respectively. The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios. 
Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[type=="test" & Model=="aby",rmse_optN_RF]` (`r table_optN_prep[type=="test" & Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[type=="test" & Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[type=="test" & Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario. CF-base was more robust to the inclusion of additional variables. Overall, the simulations present CF-base as the clear winner in estimating EONR.

@@

Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure \@ref(fig:vis-y-pred) in Appendix E for example visualizations of predicted and true yields along with RMSE values by model). Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN. Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN) show that strong predictive power of yield levels does not imply accurate prediction of EONR. Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well. While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables. Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.

@@

We examined the use of CF in the generation of site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF. However, it is important to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN. Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research. In particular, CNN is extrememly flexible in its architecture, and it is possible that other architectures than the one tried in this study may perform much better.

We also showed that the best model in predictin yields is not necessarily the best model in predicting EONR and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map. Many studies seek to predict yield level accurately using deep learning methods. Our results question the usefulness of such models in the making of management decisions. Further examinations into these issues are warranted.

>>>>

The first term on the right-hand side of Eq. \@ref(eq:eqn3) is the deterministic yield component. The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot. Also in Eq. \@ref(eq:eqn3), $\alpha$, $\beta$, and $ymax$ are spatially varying parameters that govern how yield level is determined in conjunction with the applied N rate. They reflect local cell-level production conditions, such as soil characteristics and topography. For example, $\alpha$, which represents what the yield would be when no nitrogen is applied in conjunction with $ymax$, may reflect soil organic matter and residual nitrogen from previous year's production. $ymax$, which determines the maximum yield attainable, may include other micro nutrients like phosphorus and soil depth. $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen]. Figure \@ref(fig:vis-MB-curve) presents example visualization of site-specific yield response functions for some sites.

@@

CNN leaves room for researchers to determine its architecture. We used a slightly modified version of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion." Briefly stated, explanatory variables except N rate (e.g. $\alpha_{i,j}$, $\beta_{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.The input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot. First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters each with stride one, followed by a $2 \times 2$ max-pooling layer with stride two. Then, a fully-connected rectified linear unit (ReLU) layer with sixteen neurons was added after each max-pooling layer, followed by a single ReLU neuron. Finally, multiple neurons were concatenated and fed to the fully-connected ReLU layer with sixteen neurons, followed by an output with a linear activation function. @barbosa2020modeling demonstrated that among several CNN architectures, this architecture modeled crop yield response to N rate management best. CNN was implemented in Python v3.7.6 using Pytorch v1.7.0 [@paszke2017automatic]. The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value). To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience (see Figure D.1 in Appendix D for an illustration of the convergence of training with respect to the number of epochs).

@@

Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the RMSEs of the EONR estimations and $\hat{\pi}_{def}$ obtained from the one thousand simulation rounds by ML method and modeling scenario, respectively. The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios. 
Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[type=="test" & Model=="aby",rmse_optN_RF]` (`r table_optN_prep[type=="test" & Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[type=="test" & Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[type=="test" & Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario. CF-base was more robust to the inclusion of additional variables. Overall, the simulations present CF-base as the clear winner in estimating EONR.

@@

Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure E.1 in Appendix E for example visualizations of predicted and true yields along with RMSE values by model). Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN. Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN) show that strong predictive power of yield levels does not imply accurate prediction of EONR. Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well. While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables. Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.

@@

We examined the use of CF in the generation of site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF. However, it is important to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN. Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research. In particular, CNN is extremely flexible in its architecture, and it is possible that other architectures than the one tried in this study may perform much better.

We also showed that the best model in prediction yields is not necessarily the best model in predicting EONR and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map. Many studies seek to predict yield level accurately using deep learning methods. Our results question the usefulness of such models in the making of management decisions. Further examinations into these issues are warranted.
